Communication complexity: Chapter 7 \\ Multiparty communication

### 2019-03-15 CS860-CommunicationComplexity/assignments/Chapter7.tex
Problem 8

\begin{theorem}
$D(\GIP^k) = O(\frac{n}{2^k})$.
\end{theorem}

@@

@@

>>>>

\begin{theorem}
$D(\GIP^k) = O(\frac{nk}{2^k})$.
\end{theorem}

@@

\begin{proof}
Let $\pi$ be a multiparty SMP protocol for $\Index^k$ with communication cost $c$. Suppose for a contradiction that $c < \frac{n}{k}$. Consider the following communication problem: Alice receives $A \in \{0,1\}^{n^{k-1}}$ and Bob receives $i_2,\dots, i_k$ and they need to compute $A[i_2,\dots, i_k]$. We will present a \emph{one-way} deterministic protocol for this problem using $\pi$ with cost less than $n^{k-1}$. Using the same argument as we did in Chapter $6$ for the one-way deterministic communication cost of $\Index$, we can show that this problem was one-way deterministic communication complexity at least $n^{{k-1}})$. Hence we will have reached a contradiction.

It remains to give the promised protocol. For each player $j \in \{2, \dots, k\}$ Alice enumerates the possible input $k-2$-tuples $t$ that $j$ would see the other players in $\{2,\dots, k\}$ holding, and for each such possiblity Alice sends to Bob the message $j$ would send in $\pi$ seeing $A$ and $t$. For each player this total communication cost is $cn^{k-2}$. Thus Alice sends strictly less than
$$ckn^{n-2} < n^{k-1}$$
bits it total.
Using the bits Alice sent, Bob can determine the messages that all players would sent in $\pi$ under input $A,i_2,\dots, i_k$, and can output the referees decision, computing $\Index^k$.
\end{proof}

@@

\begin{proof}
Enter a proof

\end{proof}
